Verifying Demonstrations

### 2020-03-13 paper/ZKPK.tex
Expands PK in ZKPK section

We will use the notation introduced by \citet{PKnotation}:
\begin{equation}\label{PKexample}
  \PK[\alpha, \beta, \gamma][y = g^\alpha h^\beta \land y' = \hat g^\gamma],
\end{equation}
which means that we prove knowledge of \(\alpha, \beta, \gamma\) ensuring that \(y, y'\) are of the form \(y = g^\alpha h^\beta\) and \(y' = \hat g^\gamma\), respectively.
Greek letters are known only to the prover and used for the information for which the prover wishes to prove knowledge, while all other letters are known by the verifier.

>>>>

We will use the notation introduced by \citet{PKnotation}:
\begin{equation}\label{PKexample}
  \PK[\alpha, \beta, \gamma][y = g^\alpha h^\beta \land y' = \hat g^\gamma],
\end{equation}
is \iac{PK} protocol where the prover proves knowledge of \(\alpha, \beta, 
\gamma\) ensuring that \(y, y'\) are of the form \(y = g^\alpha h^\beta\) and 
\(y' = \hat g^\gamma\), respectively.
Greek letters are known only to the prover and used for the information for which the prover wishes to prove knowledge, while all other letters are known by the verifier.
